Concept Dev for COMP study

### 2019-08-15 concept_dev.tex
fleshed out the justification

\subsection{Disciplinary Composition} One way to identify the growth and diversity of a field might be the subject areas of publications and how it changes over time .So We  calculated the disciplinary composition for all the publications and unique references from 1996-2018. These are calculated based on ASJC codes which are assigned by Scopus at journal level, i.e every publication in a journal or conference will have the same subject area. Journals or conferences can have multiple subject areas. Multidisciplinary journals such as Nature, Science, Proceedings of the National Academy of Sciences are classified as General which result in the loss of computer science articles published in those journals. Also there is a lot of ambiguity in journals/conferences with multiple ASJC codes. Following possibilities can be explored to overcome ambiguity:

>>>>

\subsection{Disciplinary Composition} One way to identify the growth and diversity of a field is by considering the count and subject areas of scientific publications in it and how these change over time. In our study of the evolution of the field of computer science, we initially used the All Science Journal Classification (ASJC) codes assigned by Scopus to journals to crudely estimate publications and unique references from 1996-2018. Accordingly, we searched for articles or conference proceedings labelled computer science (COMP), one of the 27 major subject areas in the Scopus classification system. ICOMP itself comprises 13 minor subject areas such as Hardware and Architecture and Artificial Intelligence. A limitation of the ASJC system is that every publication inherits its journal or conference subject area(s), which is problematic for a field that has had broad influence and interactions on other fields. Further, multidisciplinary journals such as Nature, Science, Proceedings of the National Academy of Sciences are classified under General and computer science articles published in those journals would be overlooked. Thus, we followed an initial subsetting of Scopus using COMP and GENERAL with an article level clustering approach. :
